---
title: 'Coursera Rep_Research: Course Project 1'
author: "Kambiet"
date: "2023-12-13"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Assignment Instructions
  1. Code for reading in the data set and/or processing the data
  2. Histogram of the total number of steps taken each day
  3. Mean and median number of steps taken each day
  4. Time series plot of the average number of steps taken
  5. The 5-minute interval that, on average, contains the maximum     number of steps
  6. Code to describe and show a strategy for imputing missing data
  7. Histogram of the total number of steps taken each day after missing values are imputed
  8. Panel plot comparing the average number of steps taken per 5-minute interval across weekdays and weekends
  9. All of the R code needed to reproduce the results (numbers, plots, etc.) in the report
  
##Step 1:Code for reading and/or processing the data


```{r, echo = TRUE}
Movedata <- read.csv("activity.csv")

```
#Exploring the nature of Movedata

```{r}
dim(Movedata)
names(Movedata)
head(Movedata)
str(Movedata)

#Evaluating and treating values in Movedata
sum(is.na(Movedata$steps))/dim(Movedata)[[1]]

#Transforming the date column in Movedata using lubridate
library(lubridate)
Movedata$date <- ymd(Movedata$date)
length(unique(Movedata$date))
```
